---
title: "Replicability in Econometrics: ARCH/GARCH Modeling"
subtitle: "NEKN34 - Computer Lab 2"
author: "Sebastian Brugger, Axel Löveråsen, Daniel Arredondo"
date: "2023-03-05"
papersize: a4
linestretch: 1.5
fontsize: 12pt
mainfont: Arial
output:
  pdf_document:
    number_sections: true
---

```{r setup, include = FALSE}
# Setup options for R Markdown
knitr::opts_chunk$set(
	echo = FALSE,
	fig.align = "center",
	fig.height = 2.4,
	fig.width = 2.7,
	message = FALSE,
	warning = FALSE
)
#geometry: margin=2.54cm
library(tidyverse)
library(moments)
library(lubridate)
library(rugarch)
library(stargazer)

# Set a theme for ggplot2
theme_set(theme_grey(base_size = 10))

# Set options
options(
  digits = 3, # limit the number of significant digits
  width  = 63 # limit the width of code output
)
```

# Introduction

This paper is meant to provide a narrow replication of results on the conditional heteroskedasticity of the yen-dollar exchange rate modeled by a ARCH models such as was done by Tse[^1^], and later by Tsue and Ho[^2^].

[^1^]: Tse, Y. K. (1998). The conditional heteroscedasticity of the yen–dollar exchange rate. Journal of Applied Econometrics, 13(1):49–55.
[^2^]: Tsui, A. K. and Ho, K.-Y. (2004). Conditional heteroscedasticity of exchange rates: further results based on the fractionally integrated approach. Journal of Applied Econometrics, 19(5):637–642.

# Data and Models

The data set used in this report includes daily yen-dollar exchange rate spanning from January 4, 1971 to January 13, 2021, totaling 12767 observations.

We compute the daily returns on nominal exchange rates $S_t$ in the same way Tse and Tsui did. The daily returns , denoted $r_t$ and represented as a percentage, are calculated as
$\begin{equation} r_t = log(\frac{S_t}{S_{t-1}}) \times 100. \end{equation}$

```{r index}
period_tse  <- list(start  = as_date("1978-01-03"), end  = as_date("1994-06-29"))
period_tsui <- list(start1 = as_date("1986-01-02"), end1 = as_date("1997-06-30"),
                    start2 = as_date("1986-01-02"), end2 = as_date("2003-02-21"))

yen_usd_rate <- read_csv("ExchangeRate.csv", skip = 11)

yen_usd_rate_fixed <- yen_usd_rate %>% mutate(date = lubridate::mdy(date))

index <- list(seq1 = seq(which(yen_usd_rate_fixed$date == period_tse$start), 
                         which(yen_usd_rate_fixed$date == period_tse$end)),
              seq2 = seq(which(yen_usd_rate_fixed$date == period_tsui$start1), 
                         which(yen_usd_rate_fixed$date == period_tsui$end1)),
              seq3 = seq(which(yen_usd_rate_fixed$date == period_tsui$start2), 
                         which(yen_usd_rate_fixed$date == period_tsui$end2)))

```

```{r, include=FALSE}


log_rate_p1 <- yen_usd_rate_fixed[index$seq1,] %>% 
    mutate(value = log(value / lag(value)) * 100)

log_rate_p2 <- yen_usd_rate_fixed %>% 
    mutate(value = log(value / lag(value)) * 100)

log_rate_p1[1,2] <- log_rate_p2[1,2] <- 0

rate_skewness1 <- moments::skewness(log_rate_p1$value)
rate_kurtosis1 <- moments::kurtosis(log_rate_p1$value)

rate_skewness2 <- moments::skewness(log_rate_p2$value)
rate_kurtosis2 <- moments::kurtosis(log_rate_p2$value)
```

Note that $r_t$ is negatively skewed and leptokurtic. 

```{r GARCH_ind1}
# GARCH Specifications
spec_mean <- list(armaOrder = c(1,0),
                  include.mean = TRUE)

spec_GARCH <- list(model = "sGARCH", # default = ’sGARCH’ (vanilla GARCH).
                   # Valid models are ’iGARCH’, ’gjrGARCH’, ’eGARCH’, ’apARCH’ and ’fGARCH’
                   
                   garchOrder = c(1, 1), # default = c(1,1).
                   # The order of the GARCH model
                         
                   submodel = NULL,      # default = NULL.
                   # In the case of the ’fGARCH’ omnibus model, valid choices are ’GARCH’, ’TGARCH’, ’GJRGARCH’, ’AVGARCH’, ’NGARCH’, ’NAGARCH’, ’APARCH’ and ’ALLGARCH’
                         
                   external.regressors = NULL, # default = NULL.
                   # A matrix of external regressors of the same length as the data
                         
                   variance.targeting = FALSE # default = FALSE.
                   # Whether to include variance targeting. It is also possible to pass a numeric value instead of a logical, in which case it is used for the calculation instead of the variance of the conditional mean equation residuals
)

# GARCH Model Fit

# Fixed conditional mean
model_fit_GARCH1 <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_GARCH,
                                                        mean.model = list(armaOrder = c(0,0),
                                                                          include.mean = TRUE)),
                                      data = log_rate_p1$value,
                                      out.sample = 0, # controls how many data points from the end to keep for out of sample forecasting
                                      solver = "solnp", solver.control = list(),
                                      fit.control = list(stationarity = 1, # controls whether to impose a stationarity constraint during estimation, which is usually closely tied to the persistence of the process
                                                         fixed.se = 0, # controls whether, for those values which are fixed, numerical standard errors should be calculated
                                                         scale = 0, # controls whether the data should be scaled prior to estimation by its standard deviation (scaling sometimes facilitates the estimation process)
                                                         rec.init = "all", trunclag = 1000))

# AR(1) conditional mean
model_fit_GARCH2 <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_GARCH,
                                                        mean.model = spec_mean),
                                      data = log_rate_p1$value,
                                      out.sample = 0,
                                      solver = "solnp", solver.control = list(),
                                      fit.control = list(stationarity = 1, 
                                                         fixed.se = 0,  
                                                         scale = 0, 
                                                         rec.init = "all", trunclag = 1000))
```

```{r GARCH_ind2}
# GARCH Specifications
spec_mean <- list(armaOrder = c(1,0),
                  include.mean = TRUE)

spec_GARCH <- list(model = "sGARCH",
                   garchOrder = c(1, 1),
                   submodel = NULL,
                   external.regressors = NULL,
                   variance.targeting = FALSE)

# GARCH Model Fit

# Fixed conditional mean
model_fit_GARCH3 <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_GARCH,
                                                        mean.model = list(armaOrder = c(0,0),
                                                                          include.mean = TRUE)),
                                      data = log_rate_p2$value,
                                      out.sample = 0,
                                      solver = "solnp", solver.control = list(),
                                      fit.control = list(stationarity = 1,
                                                         fixed.se = 0,
                                                         scale = 0,
                                                         rec.init = "all", trunclag = 1000))

# AR(1) conditional mean
model_fit_GARCH4 <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_GARCH,
                                                        mean.model = spec_mean),
                                      data = log_rate_p2$value,
                                      out.sample = 0,
                                      solver = "solnp", solver.control = list(),
                                      fit.control = list(stationarity = 1, 
                                                         fixed.se = 0,  
                                                         scale = 0, 
                                                         rec.init = "all", trunclag = 1000))
```

```{r APARCH_ind1}
spec_APARCH <- list(model = "apARCH",
                    garchOrder = c(1, 1),
                    submodel = "GARCH",
                    external.regressors = NULL,
                    variance.targeting = FALSE)

# fixed conditional mean
model_fit_APARCH1 <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_APARCH,
                                                        mean.model = list(armaOrder = c(0,0),
                                                                          include.mean = TRUE)),#,
                                                         #fixed.pars = list(delta = 2)),
                                      data = log_rate_p1$value,
                                      out.sample = 0,
                                      solver = "solnp", solver.control = list(),
                                      fit.control = list(stationarity = 1,
                                                         fixed.se = 0,
                                                         scale = 0,
                                                         rec.init = "all", trunclag = 1000))

# AR(1) conditional mean
model_fit_APARCH2 <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_APARCH,
                                                        mean.model = spec_mean),#,
                                                         #fixed.pars = list(delta = 2)),
                                      data = log_rate_p1$value,
                                      out.sample = 0,
                                      solver = "solnp", solver.control = list(),
                                      fit.control = list(stationarity = 1,
                                                         fixed.se = 0,
                                                         scale = 0,
                                                         rec.init = "all", trunclag = 1000))

# Fixed conditional mean, fixed gamma
model_fit_APARCH3 <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_APARCH,
                                                        mean.model = list(armaOrder = c(0,0),
                                                                          include.mean = TRUE),
                                                        fixed.pars = list(gamma1 = 0)),
                                      data = log_rate_p1$value,
                                      out.sample = 0,
                                      solver = "solnp", solver.control = list(),
                                      fit.control = list(stationarity = 1,
                                                         fixed.se = 0,
                                                         scale = 0,
                                                         rec.init = "all", trunclag = 1000))
```

```{r APARCH_ind2}
spec_APARCH <- list(model = "apARCH",
                    garchOrder = c(1, 1),
                    submodel = "GARCH",
                    external.regressors = NULL,
                    variance.targeting = FALSE)

# fixed conditional mean
model_fit_APARCH4 <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_APARCH,
                                                        mean.model = list(armaOrder = c(0,0),
                                                                          include.mean = TRUE)),#,
                                                         #fixed.pars = list(delta = 2)),
                                      data = log_rate_p2$value,
                                      out.sample = 0,
                                      solver = "solnp", solver.control = list(),
                                      fit.control = list(stationarity = 1,
                                                         fixed.se = 0,
                                                         scale = 0,
                                                         rec.init = "all", trunclag = 1000))

# AR(1) conditional mean
model_fit_APARCH5 <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_APARCH,
                                                        mean.model = spec_mean),#,
                                                         #fixed.pars = list(delta = 2)),
                                      data = log_rate_p2$value,
                                      out.sample = 0,
                                      solver = "hybrid", solver.control = list(),
                                      fit.control = list(stationarity = 1,
                                                         fixed.se = 0,
                                                         scale = 0,
                                                         rec.init = "all", trunclag = 1000))

# Fixed conditional mean, fixed gamma
model_fit_APARCH6 <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_APARCH,
                                                        mean.model = list(armaOrder = c(0,0),
                                                                          include.mean = TRUE),
                                                        fixed.pars = list(gamma1 = 0)),
                                      data = log_rate_p2$value,
                                      out.sample = 0,
                                      solver = "solnp", solver.control = list(),
                                      fit.control = list(stationarity = 1,
                                                         fixed.se = 0,
                                                         scale = 0,
                                                         rec.init = "all", trunclag = 1000))
```

```{r misc_ARCH}
# spec_iGARCH <- list(model = "iGARCH",
#                     garchOrder = c(1, 1),
#                     submodel = NULL,
#                     external.regressors = NULL,
#                     variance.targeting = FALSE)
# 
# model_fit_iGARCH <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_iGARCH,
#                                                         mean.model = spec_mean),
#                                       data = log_rate_p1$value,
#                                       out.sample = 0,
#                                       solver = "solnp", solver.control = list(),
#                                       fit.control = list(stationarity = 1,
#                                                          fixed.se = 0,
#                                                          scale = 0,
#                                                          rec.init = "all", trunclag = 1000))
# 
# spec_eGARCH <- list(model = "eGARCH",
#                     garchOrder = c(1, 1),
#                     submodel = NULL,
#                     external.regressors = NULL,
#                     variance.targeting = FALSE)
# 
# model_fit_eGARCH <- rugarch::ugarchfit(spec = ugarchspec(variance.model = spec_eGARCH,
#                                                         mean.model = spec_mean),
#                                       data = log_rate_p1$value,
#                                       out.sample = 0,
#                                       solver = "solnp", solver.control = list(),
#                                       fit.control = list(stationarity = 1,
#                                                          fixed.se = 0,
#                                                          scale = 0,
#                                                          rec.init = "all", trunclag = 1000))
```

```{r latex_code}
# #     mu     ar1   omega  alpha1   beta1 
# coef_garch1 <- c(-0.0115,  0, 0.0289,  0.0852,  0.8509,0,0)
# #     mu     ar1   omega  alpha1   beta1 
# coef_garch2 <- c(-0.0120,  0.0308,  0.0288,  0.0851,  0.8512,0,0) 
# #     mu     ar1   omega  alpha1   beta1  gamma1   delta 
# coef_aparch1 <- c(-0.0106,  0, 0.0311,  0.0898,  0.8575, -0.0134,  1.7417) 
# #     mu     ar1   omega  alpha1   beta1  gamma1   delta 
# coef_aparch2 <- c(-0.0108,  0.0312,  0.0307,  0.0894,  0.8582, -0.0193,  1.7498) 
# #     mu     ar1   omega  alpha1   beta1  gamma1   delta 
# coef_aparch3 <- c(-0.0110,  0, 0.0318,  0.0904,  0.8568,  0.0000,  1.7192)
# 
# latex_matrix <-t(as.matrix(rbind(coef_garch1, coef_garch2, coef_aparch1, coef_aparch2, coef_aparch3)))
# rownames(latex_matrix) <- c("mu", "ar1", "omega", "alpha1", "beta1", "gamma1", "delta")
# stargazer(latex_matrix, rownames = TRUE)

```
