---
title: "Replicability in Econometrics: ARCH/GARCH Modeling"
subtitle: "NEKN34 - Computer Lab 2"
author: "Sebastian Brugger, Axel Löveråsen, Daniel Arredondo"
date: "2023-03-05"
papersize: a4
linestretch: 1.5
fontsize: 12pt
mainfont: Arial
output:
  pdf_document:
    number_sections: true
---

```{r setup, include = FALSE}
# Setup options for R Markdown
knitr::opts_chunk$set(
	echo = FALSE,
	fig.align = "center",
	fig.height = 2.4,
	fig.width = 2.7,
	message = FALSE,
	warning = FALSE
)
#geometry: margin=2.54cm
library(tidyverse)
library(moments)

# Set a theme for ggplot2
theme_set(theme_grey(base_size = 10))

# Set options
options(
  digits = 3, # limit the number of significant digits
  width  = 63 # limit the width of code output
)
```

# Introduction

This paper is meant to provide a narrow replication of results on the conditional heteroskedasticity of the yen-dollar exchange rate modeled by a ARCH models such as was done by Tse[^1^], and later by Tsue and Ho[^2^].

[^1^]: Tse, Y. K. (1998). The conditional heteroscedasticity of the yen–dollar exchange rate. Journal of Applied Econometrics, 13(1):49–55.
[^2^]: Tsui, A. K. and Ho, K.-Y. (2004). Conditional heteroscedasticity of exchange rates: further results based on the fractionally integrated approach. Journal of Applied Econometrics, 19(5):637–642.

# Data and Models

The data set used in this report includes daily yen-dollar exchange rate spanning from January 4, 1971 to January 13, 2021, totaling 12767 observations.

We compute the daily returns on nominal exchange rates $S_t$ in the same way Tse and Tsui did. The daily returns , denoted $r_t$ and represented as a percentage, are calculated as
$\begin{equation} r_t = log(\frac{S_t}{S_{t-1}}) \times 100. \end{equation}$

```{r, include=FALSE}
yen_usd_rate <- read_csv("ExchangeRate.csv", skip = 11)
log_rate <- yen_usd_rate %>% 
    mutate(value = log(value / lag(value)) * 100,
           date  = lubridate::mdy(date)) %>% 
    filter(!is.na(value))

moments::skewness(log_rate$value)
moments::kurtosis(log_rate$value)

```

Note that $r_t$ is negatively skewed and leptokurtic. 
