---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(readxl)

# setwd("C:/Users/da3534ar-s/OneDrive/Documents/Lund University/NEKN34/Lab3")
```

# Data

```{r}
moneyincome.data <- readxl::read_xlsx("MoneyIncome.xlsx",
                          sheet = "data")
currcir.data <- readxl::read_xls("CURRCIR.xls", skip = 10)
cpiaucsl.data <- readxl::read_xls("CPIAUCSL.xls", skip = 10)
gs10.data <- readxl::read_xls("GS10.xls", skip = 10)
m2sl.data <- readxl::read_xls("M2SL.xls", skip = 10)
fedfunds.data <- readxl::read_xls("FEDFUNDS.xls", skip = 10)

income.data <- moneyincome.data %>% 
  left_join(currcir.data, by = c("t" = "observation_date")) %>% 
  left_join(cpiaucsl.data, by = c("t" = "observation_date")) %>%
  left_join(gs10.data, by = c("t" = "observation_date")) %>%
  left_join(m2sl.data, by = c("t" = "observation_date")) %>%
  left_join(fedfunds.data, by = c("t" = "observation_date")) %>% 
  rename(curr_circ = CURRCIR,
         cpi_index = CPIAUCSL,
         treas_10yr = GS10,
         m2 = M2SL,
         fedfunds_rate = FEDFUNDS)

# glimpse(income.data)
```

```{r}
summary(income.data)
```

| Variables     | Title                       | Units             | Freq    | Seasonally Adjusted? |
|---------------|-----------------------------|-------------------|---------|----------------------|
| ip            | Industrial Production Index | Index 2012=100    | Monthly | Yes                  |
| m1            | M1 Money Stock              | Billions in \$USD | Monthly | Yes                  |
| m2            | M2 Money Stock              | Billions in \$USD | Monthly | Yes                  |
| curr_circ     | Currency in Circulation     | Billions in \$USD | Monthly | No                   |
| cpi_index     | Consumer Price Index for All Urban Consumers: All Items in U.S.  | City Average, Index 1982-1984=100 | Monthly | Yes                  |
| treas_10yr    | Mkt. Yield on US Treasury Securities at 10-Year Constant Maturity | Percent | Monthly | No                  |
| fedfunds_rate | Federal Funds Effective Rate| Percent           | Monthly | No                   |



: Description of the data, sourced from [Federal Reserve Bank of St. Louis](https://fred.stlouisfed.org).

```{r}
income.ts <- timeSeries::timeSeries(data = income.data[,-1], 
                                    charvec = income.data$t)

# base::plot(x = income.data$t, y = income.data$ip, type = "l")

# log_income <- income.data %>% 
#   mutate()

# apply(as.matrix(income.data[,-1]) , 2, tseries::adf.test, alternative="s")
```

